%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Aminul Islam} \\ \vspace{1pt}
    \small +91 9064767147 $|$ \href{mailto:aminulislam03905@gmail.com}{\underline{aminulislam03905@gmail.com}} $|$ 
    \href{https://linkedin.com/in/aminulee}{\underline{linkedin.com/in/aminulee}} $|$
    \href{https://github.com/aminulislam33}{\underline{github.com/aminulislam33}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Engineering Science and Technology, Shibpur}{Howrah, India}
      {Bachelor of Technology in Electrical Engineering}{Aug. 2023 -- Present}
      \resumeSubheading
      {Al Ameen Residential Academy, Budge Budge}{South 24 Parganas, India}
      {High School}{Jul. 2020 -- Apr. 2022}
    \resumeSubheading
      {Kaliachak Abasik Mission}{Malda, India}
      {High School}{Jan. 2015 -- Feb. 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Core Member at Instruo 2025 (Annual Techno-management Fest)}{Jan 2025 -- Present}
      {Indian Institute of Engineering Science and Technology, Shibpur}{Howrah, India}
      \resumeItemListStart
        \resumeItem{Contributed to the Instruo 2025 website with a React-based frontend and Node.js backend.}
        \resumeItem{Implemented OAuth2 authentication for secure user access and third-party integrations.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Lead at Electrical Engineer’s Society (EES)}{Sept 2024 -- Present}
      {Indian Institute of Engineering Science and Technology, Shibpur}{Howrah, India}
      \resumeItemListStart
        \resumeItem{Leading the development of a web application for weekly aptitude tests under AptiCrack initiative.}
        \resumeItem{Built with React for frontend and Node.js for backend, with MongoDB as the database.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{URL Shrink} $|$ \emph{\href{https://github.com/aminulislam33/URL-Shortener}{Source Code}} $|$ \emph{Node.js, Express, MongoDB, HTML/CSS}} {}
      \resumeItemListStart
        \resumeItem{Built a URL shortener with secure user authentication and MongoDB-based URL mapping.}
        \resumeItem{Developed a minimal front-end using HTML/CSS and a robust Node.js back-end.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Student Portal} $|$ \emph{\href{https://github.com/aminulislam33/student-portal}{Source Code}} $|$ \emph{React.js, Node.js, MongoDB, Nodemailer}} {}
      \resumeItemListStart
        \resumeItem{Developed an academic dashboard for students to view marksheets, attendance, and other academic details.}
        \resumeItem{Implemented email notifications using Nodemailer and JWT-based authentication.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Chat Application} $|$ \emph{Source Code on Request} $|$ \emph{Node.js, Express, Socket.io, HTML/CSS}} {}
      \resumeItemListStart
        \resumeItem{Built a real-time text chat app with user authentication and end-to-end encryption using WebSockets.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{StreamFlix} $|$ \emph{\href{https://github.com/aminulislam33/StreamFlix}{Source Code}} $|$ \emph{React.js, Node.js, Razorpay, EJS}} {}
      \resumeItemListStart
        \resumeItem{Created a movie streaming platform with Razorpay payment integration and gated access.}
        \resumeItem{Used EJS for templating and implemented secure user authentication.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Kolkata Bus Route Viewer} $|$ \emph{Private Project} $|$ \emph{React.js, Node.js, MongoDB}} {}
      \resumeItemListStart
        \resumeItem{Built an app to help travelers find optimal bus routes within Kolkata.}
        \resumeItem{Used React for the front-end and Node.js + MongoDB for the back-end.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, C/C++, SQL (Postgres), Typescript, HTML/CSS} \\
     \textbf{Frameworks}{: Node.js, Tailwind CSS} \\
     \textbf{Developer Tools}{: Git/GitHub, Linux, Docker, Microsoft Azure, Vercel, Cloudflare} \\
     \textbf{Libraries}{: React JS, Express JS}
    }}
 \end{itemize}

 %-----------PARTICIPATION-----------
\section{Participation}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Smart India Hackathon 2024}}{}
      \resumeItemListStart
        \resumeItem{College-level qualifier for SIH 2024 with a chatbot-based multilingual ticketing system developed for the Ministry of Tourism.}
        \resumeItem{Designed to automate tourist service queries and issue tickets in regional languages for enhanced accessibility.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
